---
title: "Activité Rapide 3"
date: "26/01/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Quantitative variable analysis [Pen & paper]

The `HairEyeColor` is a R base dataset containing the "Distribution of hair and eye color and sex in 592 statistics students" :

```{r, results='asis', warning=FALSE, message=FALSE}
library(dplyr)
dfr <- tibble::as_tibble( HairEyeColor )
dfr2 <- dfr %>% 
        split(f = dfr$Sex)
        # tidyr::pivot_wider(data = ., id_cols = c("Hair", "Eye"), names_from = "Sex", values_from = "n")

women <- dfr2$Female %>% 
        select(-Sex) %>% 
        tidyr::pivot_wider(., id_cols = c("Hair"), names_from = "Eye", names_prefix = "Eye_", values_from = "n")

men <- dfr2$Male %>% 
        select(-Sex) %>% 
        tidyr::pivot_wider(., id_cols = c("Hair"), names_from = "Eye",  names_prefix = "Eye_", values_from = "n")

pander::pander(women)
pander::pander(men)

# sum(women[,-1])
# sum(men[,-1])

```

1) What is the proportion of student that have brown eye and hair ?

2) Given a female student, what is the chance that she has green eye and red hair ?

3) Given a male student, what is most likely to be his hair color ?

4) Given a student that has hazel eye and red hair, is this student more likely to be a woman or a man ?

