---
title: "Retour Blended 3"
date: "26/01/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r library step}
if(!require("pacman")){install.packages("pacman")}
```


```{r data step}
iris <- tibble::as_tibble(iris)
```


### Context

The `iris` dataset.


### 1) Data Reduction

Perform dimensionnality reduction (with a PCA) on the `iris_num` dataset and plot the 2 first dimensions of projection with the labels.

```{r PCA}
# ?iris

iris_num <- iris[ , -5]
labels <- iris[,5]
iris_num
labels

?prcomp
```


```{r prcomp}
pca_iris <- prcomp(iris_num)
str( pca_iris )

pca_iris
cumsum(pca_iris$sdev / sum(pca_iris$sdev) )
pca_iris$rotation
# pca_iris$x

plot(pca_iris$x, col = labels$Species)
```


```{r ggplot}
library(ggplot2)
ggplot(iris, aes(Sepal.Length, Sepal.Width, colour = Species)) + geom_point()

```


### 2) Clustering

Perform a cluster analysis (with a kmeans) on the `iris_num` dataset and plot the results with the cluster labels. Compare those cluster with the iris species.

```{r clustering}
iris_num
?kmeans

km_iris <- kmeans(x = iris_num, centers = 10, iter.max = 100)
km_iris
```

Decide number of groups :

```{r}
plot(1:10, cumsum(km_iris$withinss)/sum(km_iris$withinss), type ="b")
```

With 3 groups

```{r}
km_iris <- kmeans(x = iris_num, centers = 3, iter.max = 100)
km_iris

plot(iris[, 1:2], col = km_iris$cluster)
points(km_iris$centers[,1:2], col = "blue")
```


### 3) Classification

Perform a classification algorithm (with Decision Tree, see `?rpart`) on the `iris` dataset and plot the results with the cluster labels. Compare those cluster with the iris species.

```{r classification}
p_load(rpart, rpart.plot)
iris
# ?rpart

# y ~ x + z +t 
tree <- rpart(Species ~ Sepal.Length + Sepal.Width, data = iris)
tree
plot(tree)
text(tree, use.n = TRUE)

rpart.plot(tree)
```


### 4) Association Analysis

```{r, message=FALSE, warning=FALSE}
pacman::p_load(arules, arulesViz)
data("Groceries", package = "arules")

?Groceries
str(Groceries)
summary(Groceries)
```

```{r scatter plot of association relation}
rules <- apriori(Groceries,
           parameter = list(supp = 0.001, conf = 0.75))
# summary(rules)
inspect(rules[1:10,])
plot(rules)
```

```{r graph association graph}
# Graph of top 20 rules
plot(rules[1:20,], 
  method = "graph", 
  control = list(type = "items"))
```


```{r parallel coordinate association plot}
# Parallel coordinates plot of top 20 rules
plot(rules[1:20], 
  method = "paracoord", 
  control = list(reorder = TRUE))
```


```{r matrix association plot}
# Matrix plot of antecedents and consequents
plot(rules[1:20], 
     method = "matrix", 
     control = list(reorder = TRUE))
```


```{r grouped association plot}
# Grouped matrix plot of antecedents and consequents
plot(rules[1:20], method = "grouped")
```


### 5) Regression Analysis

Using the iris dataset `iris_train` dataset, build a regression model (a simple linear model with `stats::lm()`) to predict the length of the iris sepals (variable `Sepal.Length`) :

```{r create the train set}
set.seed(456)
train_index <- sample(1:150, 120)
iris_train <- iris[ train_index , ]
table(iris_train$Species)
iris_x_test <- iris[-train_index , -1]
iris_y_test <- iris[-train_index , 1]
```

```{r train the model}
iris_train
```

Test you model on the test set `iris_x_test` and compare your results using `iris_y_test`. How good is your model ?

```{r test the model}
iris_x_test
iris_y_test
```


### 6) Sequential Patterns

Adapt the following code to compare several modelisation of seqential pattern mining (1 or 2 states) :

```{r HMM data}
pacman::p_load(pacman, depmixS4)
data(speed)
str(speed)
?depmixS4::speed
```


```{r HMM data plot}
plot(ts(speed[, 1:3]), main = "speed data")
```


```{r HMM model}
model1 <- depmix(list(rt ~ 1, corr ~ 1), 
            data = speed, 
            nstates = 1,
            family = list(gaussian(), 
              multinomial("identity")))
fm1 <- fit(model1, verbose = FALSE)
```


### 7) Text Mining

cf video

