---
title: "TP3 - Data Mining"
output: 
  html_document:
          toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Exercise 1 : R


In this exercise, you will explore the different types of data that can be loaded into
R for processing.

__Overview__

R has tremendous flexibility in reading data. This exercise will allow you to load internal
data sets, files, web pages (webscraping) and XML. We will also load data from a
nonrelational (NoSQL) data source.


### Major Step 1: Reviewing the first data set

1.  Install  RStudio
2.  Double-click RStudio on the desktop. In RStudio, cerate and open the file  Exo1. Add
commands to the file according to the instructions that follow in this exercise, and
execute each command as you move through the steps.
3.  At the console prompt, type library() to view all loaded packages. A list of packages will appear in a window above the console window.

```{r}
library()

sessionInfo()
loadedNamespaces()
(.packages())
```

4. Use the command to list all of the data sets available in these loaded packages.

```{r ls}
?data
?datasets

# data()
```


5.  Load the AirPassengers data set into memory.

```{r}

```


6.  View the AirPassengers data set. Which years are covered by the data set?

```{r}
```


7.  Load some other of the available data sets into memory and view them. e.g. data(BJsales)

```{r}

```

8.  When you have loaded a number of data sets into memory, list all loaded data sets.

9.  Remove the AirPassengers  data set from memory and confirm that it has been removed.

```{r}

```


10. Remove all loaded data sets from memory.

```{r}
# data("AirPassengers")
ls()
rm(list = ls())
```


11. View data sets available in the rpart package.


### Major Step 2: Loading an external file into R

12. View the current working directory in R.

13. Load .csv file into memory in R, specifying appropriate parameters.

14. View the loaded data in a data viewer. When you have finished, remove the data from memory.

16. Give column headings to the first few columns.


### Major Step 3: Loading data from MongoDB

17.  Install (`MongoDB` archived in CRAN) -> `mongolite`. To start the MongoDB server, double-click the mongodb server icon on your desktop.

18.  To start the MongoDB client, double-click the mongodb client icon on your
desktop.
You will see the command prompt appear and connect to the database test. is the name of the default database.

19.  Create a database named Rainforest

20.  Create and insert three documents into the database rainforest
using the following commands.

lesmiserables = {_id :1, Title : "Les Miserables", Director : "Tom Hooper", RunTime : 158}
db.video_recordings.insert(lesmiserables)

skyfall ={_id :2, Title : "Skyfall", Director : "Sam Mendes", RunTime : 137}
db.video_recordings.insert(skyfall)

thetallman ={_id :3, Title : "The Tall Man", Director : "Raoul Walsh", RunTime : 117}
db.video_recordings.insert(thetallman)


View you inserted documents:

22. Find the recording that has a runtime of 137 minutes:
23.  Return to RStudio.
24.  Load the RMongo package into R:

25. View RMongo help:

26. Connect to the database:
27. Query the collections in the MongoDB database:
28. Query which recordings have a runtime of 137 minutes:
29. Close the connection:

### Major Step 4: Loading a web page into R (webscraping)


30.  Load a web page into R and view it (data science from wikipedia)
31. View the loaded data

32. Load an HTML table from a website into R (http://en.wikipedia.org/wiki/List_of_countries_by_population
33. View the loaded data (the 1st element):


