---
title: "TP1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r lib}
library(tidyverse)
```


## Exercice 2

### Load data

```{r base R}
scores <- utils::read.csv(file = "../../data-raw/tp1_2.csv", sep = ";", skip = 2)
scores
```


```{r load data}
scores <- readr::read_csv2(file = "../../data-raw/tp1_2.csv")
scores
```



```{r datapasta way}
# scores <- 
# 
# scores
```

1) 

Les instructions de bases :

* table --> occurence
* prop.table --> pour convertir une table en proportions

* plot

* summary
* mean, median, quartile, quantlile, min, max, sd, var

```{r stats}
str(scores)

summary(scores)
mean(scores$Score)
median(scores$Score)
```

1) Distribution

```{r}
table(scores$Score)
prop.table( table(scores$Score) ) * 100
```

2) Graphique

```{r distribution plot}
plot( table(scores$Score) )
plot( prop.table( table(scores$Score) ) )
```

3) Ggplot histogramme

```{r}
library(dplyr)
scores %>%
        ggplot(aes(x = Score)) +
        geom_histogram(bins = 7, colour = "black", show.legend = FALSE)

# , binwidth = c(rep(7, 5), 5, 14)

plot( cut(scores$Score, 7) )
# levels(cut(scores$Score, 7))
```

```{r}
scores %>%
        ggplot(aes(x = Score)) +
        geom_histogram(bins = 9, colour = "black", show.legend = FALSE)
```

5) The mode are 36, 41 and 44 :

```{r}
scores %>%
        ggplot(aes(x = Score)) +
        geom_histogram(binwidth = 1, colour = "black", show.legend = FALSE)

names(table(scores$Score))[table(scores$Score) == max(table(scores$Score))]
# as.data.frame( table(scores$Score) )
```

6) median quartile 

```{r stats robustes}
median(scores$Score)
stats::quantile(x = scores$Score, c(0.25, 0.5, 0.75))
```

7) mean standard deviation

```{r stats}
mean(scores$Score)

sd(scores$Score)

var(scores$Score)

sqrt( var(scores$Score) )

# boxplot((scores$Score))
```


## Exercice 3

```{r clean up env}
rm(list = ls())
```

In a survey on the perception of the causes of road accidents, the following question was asked: Do you think that mechanical failures are a source of accidents?
The subjects had to respond on a scale from 0 to 10 in which the score 0 corresponds to "never", the score 5 to "sometimes" and the score 10 to "always".
Of the 160 subjects interviewed, here is the distribution of responses for men and women.

```{r load data}
dframe <- data.frame(
        score = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
        women = c(1, 3, 8, 10, 9, 12, 12, 8, 9, 7, 1),
        men = c(2, 2, 4, 4, 8, 12, 13, 11, 10, 9, 5)
)
dframe
```

```{r}
plot(x = dframe$score, y = dframe$women, col = "blue")
points(x = dframe$score, y = dframe$men, col = "red")
```


```{r}
ggplot(dframe, aes(x = score, y = women, colour = "red")) +
        geom_point() +
        geom_point( aes(x = score, y = men, colour = "blue"))+
        xlab("Women and men scores") +
        ylab("Frequency")
```

```{r}
ggplot(dframe, aes(x = score, y = women, fill = "red")) +
        geom_col(alpha = .5) +
        geom_col(aes(x = score, y = men, fill = "blue"), alpha = .5)+
        xlab("Women and men scores") +
        ylab("Frequency")
```

Conclusion : From the barplot it seems men are more likely to think that mechanical failures are a source of accidents than women.


```{r}
# dframe_longer <- pivot_longer(dframe, cols = c("men", "women"))
# 
# ggplot(dframe_longer, aes(x = name, y = value, colour = "red")) +
# #         geom_boxplot() 
# 
# # ggplot(dframe_longer, aes(x = name, y = value, colour = "red")) +
# #         geom_boxplot() 
# 
# 
#         geom_point( aes(x = score, y = men, colour = "blue"))+
#         xlab("Women and men scores") +
#         ylab("Frequency")
```


## Exercice 4

```{r husband wife age data}
hw_age <- tribble(
        ~husband, ~wife,
        20, 20,
        25, 24,
        25, 22,
        31, 29,
        18,20,
        25,24,
        32,31,
        26,25,
        22,21,
        24,24,
        24,22,
        25,26,
        27,22,
        20,18,
        18,19,
        23,21,
        23,23,
        34,35,
        45,43,
        23,22,
        22,21,
        20,22,
        21,22,
        34,32,
        21,20,
        32,30, 
        45,44,
        33,32,
        31,30, 
        33,31,
        36,35,
        28,27, 
        27,26,
        29,28,
        21,21,
        22,20,
        24,23,
        31,29,
        33,30
)
hw_age
```

