---
title: "Activité Rapide 2"
date: "13/01/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Quantitative variable analysis [Pen & paper]

Suppose you have some ratings (on a 1-10 scale, 10 being the best) of a product $\{1, 1, 5, 5, 5, 5, 9, 9\}$.

a) Represent those results in a contingency table.
b) Draw a barplot using the previous table.
c) Find the mean of the ratings.
d) Find the median of the ratings.
e) Find the mode of the ratings.


### Qualitative variable analysis

Suppose you have some products $\{$prodA, prodA, prodB, prodB, prodB, prodB, prodC, prodC$\}$.

a) Represent those results in a contingency table.
b) Draw a barplot using the previous table.
c) What is the mean of number of sold items  ?
c) What is the median of number of sold items ?
c) What is the mode of number of sold items ?

### With R for the qualitative data

a) Contingency table

Concatenate et structure de x :

```{r contingency table}

```

b) ggplot

```{r ggplot}

```

c) statistics

```{r stats}

```

