---
title: "Retour Blended 2"
date: "13/01/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### 1) Basics

Given a serie $X = \{1, 1, 1, 5, 5, 5, 5, 5, 5, 5, 5, 5\}$ (three 1, nine 5), compute __by hand__ the following statistics :

  * mean
  * median
  * variance
  * standard deviation
  * mode
  * quartiles (1, 2, 3, 4)
  * min
  * max

__Use R__ to check your results :

```{r stats}
x <- rep(c(1,5), c(3,9))
mean(x)
median(x)
var(x)
# sd
sd(x) ; # sqrt( var(x) )
quantile(x, probs = c(0.25, 0.5, 0.75))
min(x)
max(x)

quantile(c(1, 2, 3, 3), probs = c(0.25, 0.5, 0.75))
median(c(1,1,3))
```


### 2) Find one serie for every following conditions :

  * mean(x) = 2
  * median(x) = 3
  * mode(x) = 5
  * var(x) = 1


### 3) Find one serie for every following conditions :

  * mean(x) > median(x)
  * mode(x) > mean(x)
  * median(x) > mode(x)
  
  
### 4) Normalisation - Z score

Normalise the following serie (so that the mean is null and the variance is 1) :

  * $Y = \{1, 3, 5\}$

  * the one bellow using R :
  
```{r Z score}
set.seed(123)
x2 <- sample(1:10, 10, replace = TRUE)
x2
```


### 5) "Bell curve" and distance from the mean

Generate a sample of 100 real numbers obtained from a normal distribution. Find out the percentage of points within 1, 2 and 3 standard deviation of the mean.

```{r standard deviation control - sigma control}
set.seed(456)
s <- rnorm(n = 100)
s
```

